\Sof{TBA - New Titles in the comments}

### 2020-05-07 paper/icsme20.tex
t2v

\section{Threats to Validity}\label{sec:threats}
%
The following section presents the potential threats to the validity of this
study.
%
\\\textit{\textbf{Construct:}} The maintainability formula was inferred based 
on the BCH's reports. The high amount of different projects and backgrounds 
may require other maintainability standards. However, BCH does use a 
representative benchmark of closed and open-source software projects to compute 
the thresholds for each maintainability guideline~\cite{Visser:2016:OREILLY, Baggen2012}.
The way how maintainability is being calculated - mean of all guidelines - is
a preliminar measure to show how the maintainability is overall affected. Nevertheless,
in some cases the maintainability for the two versions might be the same but have
different causes, i.e., being affected by different guidelines. 
%
\\\textit{\textbf{Internal:}} The security patches dataset provided by previous
work~\cite{Reis:2017:IJSSE} was collected based on the messages of GitHub
commits produced by project developers to classify the changes performed by them
to fix security flaws. This approach discards security patches that were
not explicit in commits messages. Pontas et. al\cite{10.1109/MSR.2019.00064} dataset
has patches that were manually mined in software repositories. Being a manual technique,
the search might led to wrong associations between vulnerabilities and code snippets. 
When comparing security changes versus regular changes, our study does not take into consideration that 
developers may patch the issue quickly and later proceed to refactor.
We assume that vulnerabilities are patched once or in different parts consecutively.
Baseline commits are retrieved randomly by selecting one commit with an 
approximate size from the same
project of a given security patch. This approach softens the differences
that may result from the characteristics of each project. However,
maintainability may still be affected by the developers' experience, coding
style and software contribution policies which is not evaluated in this study.
Furthermore, this evaluation considers that $998$ regular commits are enough to
alleviate random irregularities in the maintainability differences of the
baseline. 
%
\\\textit{\textbf{External:}} We use a dataset that only comprises patches of open-source software.
However, the methodology requires to access data that is not publicly available.
Thus, our findings may not extend to non-open source software. Different programming 
languages may require different coding practices to address software safety. The 
dataset comprises more commits in Java, i.e., the dataset may not be representative 
of the population regarding programming languages. Our approach does not consider 
security patches in any other languages but English.

>>>>

\section{Threats to Validity}\label{sec:threats}
%
The following section presents the potential threats to the validity of this
study.
%
\\\textit{\textbf{Construct:}} The maintainability formula was inferred based 
on the BCH's reports. The high amount of different projects and backgrounds 
may require other maintainability standards. However, BCH does use a 
representative benchmark of closed and open-source software projects to compute 
the thresholds for each maintainability guideline~\cite{Visser:2016:OREILLY, Baggen2012}.
Maintainability is computed as the mean of all guidelines. A patch can
have the same impact on the overall maintainability of both software versions 
- non-vulnerable and vulnerable - but not necessarily on the same 
guidelines.
%
\\\textit{\textbf{Internal:}} The security patches dataset provided by previous
work~\cite{Reis:2017:IJSSE} was collected based on the messages of GitHub
commits produced by project developers to classify the changes performed by them
to fix security flaws. This approach discards security patches that were
not explicit in commits messages. Pontas et. al\cite{10.1109/MSR.2019.00064} dataset
has patches that were manually mined in software repositories and, consequently,
wrong associations may have been performed between vulnerabilities and code snippets. 
The dataset also included floss-refactorings. Both cases were manually inspected
and deleted from the dataset. Thus, this study does not consider that a
developer may perform a patch quickly and later proceed to the refactor.
Baseline commits are retrieved randomly by selecting one commit with an 
approximate size and from the same project of a given security patch. 
This approach softens the differences
that may result from the characteristics of each project. However,
maintainability may still be affected by the developers' experience, coding
style and software contribution policies which is not evaluated in this study.
Furthermore, this evaluation considers that $998$ regular commits - any kind
of commit - are enough to
alleviate random irregularities in the maintainability differences of the
baseline. 
\\\textit{\textbf{External:}} We use a dataset that only comprises patches of open-source software.
However, the methodology requires to access data that is not publicly available.
Thus, our findings may not extend to non-open source software. Different programming 
languages may require different coding practices to address software safety. The 
dataset comprises more commits in Java, i.e., the dataset may not be representative 
of the population regarding programming languages. Our approach does not consider 
security patches in any other languages but English.
